Treatment heterogeneity in comparative effectiveness of teriparatide vs bisphosphonates: multi-database cohort study

### 2021-12-03 submission/manuscript.rmd
prepare results figures except risk stratified

```{r, echo=FALSE, message=FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)

@@

@@

>>>>

```{r, echo=FALSE, message=FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)
library(here)

@@

***[ Introductory stuff for Table 1 !! ]***

@@

\newpage
```{r overallCovariateBalance, cache = TRUE, echo = FALSE, fig.cap="Calibrated overall results"}
grid::grid.raster(tiff::readTIFF(here("figures/OverallCovariateBalance.tiff")))
```

\newpage
```{r overallPsDensity, cache = FALSE, echo = FALSE, fig.cap="Calibrated overall results"}
grid::grid.raster(tiff::readTIFF(here("figures/OverallPsDensity.tiff")))
```

\newpage
```{r overallNcPlot, cache = FALSE, echo = FALSE, fig.cap="Overall negative control plot."}
grid::grid.raster(tiff::readTIFF(here("figures/OverallNcPlot.tiff")))
```
